The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
saving Conc while I pause

<!--QW: I am not very happy with this paragraph, but it's a start -->

Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data, thus allowing us to ground our broader discussion of
multilayer networks in the context of observed animal social networks.

>>>>

<!--QW: I am not very happy with this paragraph, but it's a start -->
Multilayer networks are complicated in that they can incorporate data as varied as social interactions, landscape features, and seasons, all of which exist at different scales and units of measurement. 
Our analysis of caribou multilayer networks incorporated high resolution GPS telemetry data and
spatial landcover data is grounded in the context of observed animal social networks, as the scales we chose to explore are ones that can be observed as has traditionally been done.
